04_DESeq_sexes

### 2019-06-16 analysis/04_DESeq2_sexes.Rmd
work in progress

pdf("../figures/sexes/plottotalDEGs-1.pdf", width = 12, height = 10)
plot(myDEGs)
dev.off()

@@

@@

```{r candidates, eval =F}
plotcandidates(dds.female_hypothalamus, a.colData, "female hypothalamus")
plotcandidates(dds.female_pituitary, "female pituitary")
plotcandidates(dds.female_gonad, "female gonad")
plotcandidates(dds.male_hypothalamus, "male hypothalamus")
plotcandidates(dds.male_pituitary, "male pituitary")
plotcandidates(dds.male_gondad, "male gonad")
```

@@

```{r correlationheatmaps, eval = T}
colData.female_hypothalamus <- subsetcolData(a.colData,  "female_hypothalamus")
colData.female_pituitary <- subsetcolData(a.colData,  "female_pituitary" )
colData.female_gonad <- subsetcolData(a.colData,  "female_gonad" )
colData.male_hypothalamus <- subsetcolData(a.colData,  "male_hypothalamus" )
colData.male_pituitary <- subsetcolData(a.colData,  "male_pituitary"  )
colData.male_gondad <- subsetcolData(a.colData,  "male_gonad")

plotcorrelationheatmaps(dds.female_hypothalamus, colData.female_hypothalamus ,"female hypothalamus: hatch, nest bldg., lay and day-before-hatch cluster")
plotcorrelationheatmaps(dds.female_pituitary, colData.female_pituitary, "female pituitary: clustering suggests an internal clock effect")
plotcorrelationheatmaps(dds.female_gonad, colData.female_gonad,  "female gonad: highly correlated across incubation and early nestling care")
plotcorrelationheatmaps(dds.male_hypothalamus, colData.male_hypothalamus, "male hypothalamus: 100% correlated across most parental care stages")
plotcorrelationheatmaps(dds.male_pituitary, colData.male_pituitary, "male pituitary: non-parental males are most different")
plotcorrelationheatmaps(dds.male_gondad, colData.male_gondad, "male gonad: non-parental males are most different")
```

>>>>

pdf("../figures/sexes/plottotalDEGs-1.pdf", width = 12, height = 10)
plot(myDEGs)
dev.off()
```

@@

## make col data for candidate genes and heatmaps

```{r coldata, eval =T}
colData.female_hypothalamus <- subsetcolData(a.colData,  "female_hypothalamus")
colData.female_pituitary <- subsetcolData(a.colData,  "female_pituitary" )
colData.female_gonad <- subsetcolData(a.colData,  "female_gonad" )
colData.male_hypothalamus <- subsetcolData(a.colData,  "male_hypothalamus" )
colData.male_pituitary <- subsetcolData(a.colData,  "male_pituitary"  )
colData.male_gondad <- subsetcolData(a.colData,  "male_gonad")
```

@@

```{r candidates, eval =T}
plotcandidates(dds.female_hypothalamus, colData.female_hypothalamus, "female hypothalamus")
plotcandidates(dds.female_pituitary, colData.female_pituitary,  "female pituitary")
plotcandidates(dds.female_gonad, colData.female_gonad,  "female gonad")
plotcandidates(dds.male_hypothalamus, colData.male_hypothalamus, "male hypothalamus")
plotcandidates(dds.male_pituitary,  colData.male_pituitary, "male pituitary")
plotcandidates(dds.male_gondad, colData.male_hypothalamus , "male gonad")
```

@@

```{r correlationheatmaps, eval = F}
plotcorrelationheatmaps(dds.female_hypothalamus, colData.female_hypothalamus ,"female hypothalamus: hatch, nest bldg., lay and day-before-hatch cluster")
plotcorrelationheatmaps(dds.female_pituitary, colData.female_pituitary, "female pituitary: clustering suggests an internal clock effect")
plotcorrelationheatmaps(dds.female_gonad, colData.female_gonad,  "female gonad: highly correlated across incubation and early nestling care")
plotcorrelationheatmaps(dds.male_hypothalamus, colData.male_hypothalamus, "male hypothalamus: 100% correlated across most parental care stages")
plotcorrelationheatmaps(dds.male_pituitary, colData.male_pituitary, "male pituitary: non-parental males are most different")
plotcorrelationheatmaps(dds.male_gondad, colData.male_gondad, "male gonad: non-parental males are most different")
```
